---
title: "Data Science"
format: html
editor: visual
---

## Part 1

1.  What do you think being a data scientist is about?

    - Helping organizations interpret and utilize large amounts of data in a meaningful manner (prediction, prevention, analysis etc.)

2.  What differences/similarities do you see between data scientists and statisticians?

    - Statisticians emphasize more on the theoretical analytics and math portions of the field, whereas data scientists are likely to leverage programming more as well as place emphasis on final company/business goals.

    - While statisticians might prefer statistical efficiency/optimization and validity, data scientists are more likely to tradeoff absolute accuracy to accommodate real world constraints like monetary or computing costs.

3.  How do you view yourself in relation to these two areas?

    - Its difficult to be a data scientist without having solid statistical foundations, so I believe in first learning and doing your best at mastering theoretical concepts, but then honing in on the application aspect (specifically ML these days).

## Part 2

Given data y

```{r}
y <- density(iris$Petal.Width)
```

Identify details

```{r}
class(y)
typeof(y)
str(y)
```

Plotting y

```{r}
#| echo: false
plot(y)
```
